\documentclass{resume} 
\usepackage{bookmark}
\usepackage{hyperref}
\usepackage{setspace}


\begin{document}
  \setstretch{.95}
  \name{Marlon Calvo}
  \contact{Winter Springs, FL}{(305)-490-2892}{marloncalv98@gmail.com}{linkedin.com/in/marloncalvo}{github.com/marloncalvo}
  \begin{fieldlist}{Work Experience}
    \field
      {Aug 2020}
      {University of Central Florida}
      {Orlando, FL}
      {Undergraduate Learning Assistant, Computer Science}
      {
        \begin{itemize}
          \setlength\itemsep{0em}
          \item Host review lectures and office hours on algorithm and data structures for 400 students. 
        \end{itemize}
      }


      \field
        {Feb 2019}
        {Siemens Energy}
        {Orlando, FL}
        {Software Engineering Intern}
        {
          \begin{itemize}
            \setlength\itemsep{0em}
            \item Improved performance by 2-5x, via overhauled multiprocessing algorithms and enhanced system design, for numerical analysis application (10-15k computations per month).
            \item Developed graph algorithms for analyzing large blade topologies, enabling automation of complex fluid simulations.
            \item Innovated frontend build system for Matlab's C transcompiler, saving up to 80\% developer time lost due to compilation and testing issues.
            \item Led design, implementation, and a portion of project management to rebuild legacy application for a large, company-wide, external customer project.
          \end{itemize}
        }

  \end{fieldlist}
  \begin{fieldlist}{Projects}
    \fieldnotitle
      {Aug 2020}
      {OpenJML String Support}
      {\href{http://www.openjml.org/}{openjml.org}}
      {
        \begin{itemize}
          \item Implementing support for string program verification, a necessary feature for proving algorithms.
          \item OpenJML is a large, open-source, program verification tool used for cybersecurity at Amazon.
        \end{itemize}
      }

    \fieldnotitle
      [Apr 2020]
      {Mar 2020}
      {Parking Manager}
      {\href{https://github.com/cop4331-spr2020-team/contact-manager}{github.com/cop4331-spr2020-team/contact-manager}}
      {
        \begin{itemize}
          \setlength\itemsep{0em}
          \item Built university parking administration system with administrative and analytics portals, alongside iOS client app.
          \item Led backend/frontend development and was project manager for a team of 6.
          \item Engineered backend (NodeJS, MongoDB, Redis), backend API, and frontend (React).
        \end{itemize}
      }

    \fieldnotitle
      [Apr 2020]
      {Mar 2020}
      {Quantifiable Queue}
      {\href{https://github.com/marloncalvo/quantifiable-queue}{github.com/marloncalvo/quantifiable-queue}}
      {
        \begin{itemize}
          \item Innovated a high-performance, thread-safe queue algorithm on a newly proposed correctness condition.
          \item Outperforms JDK implementation (MS-queue) by $>$1 order(s) of magnitude in OP/s.
        \end{itemize}
      }



  \end{fieldlist}
  % \section{Projects}
  %   \subsection{Quantifiable Queue}
  %     Innovated a high-performance, thread-safe queue based on a newly proposed correctness
  %     condition that outperforms JDK implementation (MS-queue) by $>$1 order of magnitude
  %     in OP/s.
  %   \subsection{Simple C Compiler}
  %     Built compiler for subset of C grammar, in C, utilizing parse trees, static typing, stacks,
  %     CFGs, into LLVM to support functions, recursions, loops, and other basic features.
  %   \subsection{Parking Manager}
  %     Engineered the backend (NodeJS), database (MongoDB \& Redis), and frontend (ReactJS) of university parking administrative system
  %     with managerial and analytics portal. System included a client iOS application to report 
  %     infractions.
  \begin{fieldlist}{Education}

    \field
      {Aug 2018}
      {University of Central Florida}
      {Orlando, FL}
      {Bachelor of Science (BS), Computer Science}
      {
        \begin{itemize}
          \setlength\itemsep{0em}
          \item \textbf{GPA}: 3.86 / 4.00
          \item \textbf{Coursework}: Computer Vision, Deep Learning for Computer Vision, Parallel Computing Architecture and Algorithms, Computer Graphics, Competitive Programming Contests
        \end{itemize}
        
      }

  \end{fieldlist}
  \section{Skills}
      \begin{itemize}
        \item \textbf{Languages}: Java, Python, C/C++, Go, JavaScript, Matlab
        \item \textbf{Technologies}: NodeJS, MongoDB, Redis, React, SQL, JavaFX, Qt, Keras, Unix
      \end{itemize}
\end{document} 